---
title: "R Notebook"
output: html_notebook
---

# Libraries
```{r}
library(broom)
library(cowplot)
library(ggpubr)
library(grid)
library(tidyverse)
library(lubridate)
library(ncdf4)
library(Peacock.test)
library(raster)
library(readxl)
library(rgdal)
library(sp)
library(stargazer)
library(zoo)
```

# Variables
```{r variables}
threshold <- 1
strip.background <- 'grey90'
```

# Load data

## Load landslides

### Load landslide locations
```{r load_landslides}
size.levels <- c('medium', 'large', 'very_large')
location.accuracy.levels <- c('exact', '1km', '5km', '10km', '25km', 
                              '50km', '100km', '250km', 'unknown')
allowed.triggers <- c('downpour', 'rain', 'flooding', 'continuous_rain')
slide.list <- read_csv("data/landslide/landslides.original.csv",
                       col_types = list('datetime' = col_datetime(format = "%m/%d/%y %H:%M"),
                                        'type' = col_factor(),
                                        'trigger' = col_factor(),
                                        'size' = col_factor(ordered = T,
                                                            levels = size.levels)
                                       )
) %>%
  rename(slide.id=id, slide.date=datetime)
```

### Load landslide details from the NASA Glabal Landslide Catalog (GLC)
```{r read_details}
# Read in NASA GLC for additional landslide details
slide.details.ct <- list('location_accuracy' = col_factor(ordered=T,
                                                          levels = location.accuracy.levels))
slide.details <- read_csv("data/landslide/nasa.glc.export.csv",
                          col_types = slide.details.ct) %>%
  dplyr::select(slide.id = event_id, location_accuracy, event_title, admin_division_name)
```

### Load Koppen climate classification
```{r read_koppen}
# Read in Koppen climate classification
koppen.levels <- seq(1, 30)
koppen.labels <- c('Af: Tropical, rainforest',
                   'Am: Tropical, monsoon',
                   'Aw: Tropical, savannah',
                   'BWh: Arid, desert, hot',
                   'BWk: Arid, desert, cold',
                   'BSh: Arid, steppe, hot',
                   'BSk: Arid, steppe, cold',
                   'Csa: Temperate, dry summer, hot summer',
                   'Csb: Temperate, dry summer, warm summer',
                   'Csc: Temperate, dry summer, cold summer',
                   'Cwa: Temperate, dry winter, hot summer',
                   'Cwb: Temperate, dry winter, warm summer',
                   'Cwc: Temperate, dry winter, cold summer',
                   'Cfa: Temperate, no dry season, hot summer',
                   'Cfb: Temperate, no dry season, warm summer',
                   'Cfc: Temperate, no dry season, cold summer',
                   'Dsa: Cold, dry summer, hot summer',
                   'Dsb: Cold, dry summer, warm summer',
                   'Dsc: Cold, dry summer, cold summer',
                   'Dsd: Cold, dry summer, very cold winter',
                   'Dwa: Cold, dry winter, hot summer',
                   'Dwb: Cold, dry winter, warm summer',
                   'Dwc: Cold, dry winter, cold summer',
                   'Dwd: Cold, dry winter, very cold winter',
                   'Dfa: Cold, no dry season, hot summer',
                   'Dfb: Cold, no dry season, warm summer',
                   'Dfc: Cold, no dry season, cold summer',
                   'Dfd: Cold, no dry season, very cold winter',
                   'ET: Polar, tundra',
                   'EF: Polar, frost')
slide.koppen <- read_csv("climate_gis/landslide_koppen.csv") %>%
  transmute(slide.id, koppen = Beck_KG_V1) %>%
  mutate(koppen = factor(koppen, levels = koppen.levels, labels = koppen.labels))

slide.koppen %>% group_by(koppen) %>% tally %>% arrange(desc(n))
```
Only the Csb classification meets the qualification of n>50 for including a climate-specific threshold. This corresponds with the Csb (Mediterranean, cool) intensity-duration threshold in Guzzetti (2008).

### Load landslide coordinates retrieved from Google Earth
```{r read_scarp}
# Read in Google Earth scarp coordinates
get_decimal_coord <- function (coord_str, lat) {
  col <- ifelse(lat, 1, 2)
  coord_str <- str_split(coord_str, ', ', simplify=T)
  coord_dms <- map_dbl(coord_str[,col], 
                       ~possibly(~as.numeric(char2dms(., chd = "°", chm = "\'", chs = "\"")), 
                                 NA_real_)(.))
  coord_dms
}
slide.scarp <- read_excel("data/landslide/verified.locations.xlsx", sheet = 'Visible Scarps') %>%
  dplyr::select(slide.id = ID, glc.lat=`Lat.`, glc.lon=`Long.`, coord.str=`Google Earth Coordinates`) %>%
  mutate(ge.lat = get_decimal_coord(coord.str, lat=T),
         ge.lon = get_decimal_coord(coord.str, lat=F),
         ge.lat = ifelse(is.na(ge.lat), glc.lat, ge.lat),
         ge.lon = ifelse(is.na(ge.lon), glc.lon, ge.lon),
         is.exact = T)
```

### Join landslides
```{r join_slide}
#
slide.full <- slide.list %>%
  left_join(slide.details, by = c('slide.id')) %>%
  left_join(slide.scarp %>% dplyr::select(slide.id, ge.lat, ge.lon, is.exact), by='slide.id') %>%
  left_join(slide.koppen, by = 'slide.id') %>%
  mutate(slide.index = row_number()) 
slide.allprecip <- slide.full %>%
  filter(location_accuracy <= '10km' | is.exact, # Apply study restrictions
         trigger %in% allowed.triggers) %>%
  droplevels() %>%
  mutate(is.exact = ifelse(is.na(is.exact), F, is.exact), # Use exact coordinates over glc
         lat = ifelse(!is.na(ge.lat), ge.lat, lat),
         lon = ifelse(!is.na(ge.lon), ge.lon, lon),
         type = fct_collapse(type,
                             'Mudslide or debris flow' = c('mudslide', 'debris_flow'),
                             'Rock fall' = 'rock_fall',
                             other_level = 'Landslide')) %>%
  droplevels()

# Check data
summary(slide.allprecip)
```


## Load precipitation
```{r}
precip.mrms <- read_table2("data/precipitation/All_Landslides_PRE_MRMS.txt",
                          col_names = c('year', 'month', 'day', 'hour', 
                                        seq(1, nrow(slide.full))
                                        )
                          ) %>%
  mutate(datetime = ymd_h(str_c(year, '-', month, '-', day, ' ', hour)),
         source = 'MRMS',
         delta.t = 1) %>%
  dplyr::select(-year, -month, -day, -hour) %>%
  gather(key = 'landslide', value = 'precipitation', -datetime, -source, -delta.t) %>%
  mutate(landslide=as.integer(landslide),
         precipitation = ifelse(precipitation < 0, NA, precipitation)) %>%
  left_join(slide.full %>% dplyr::select(slide.id, slide.index), 
            by=c('landslide'='slide.index')) %>%
  dplyr::select(-landslide)

precip.nldas <- list.files(path = 'data/precipitation/nldas/verified', 
                           pattern = '^nldas.*.csv', full.names = T) %>%
  map(read_csv) %>%
  bind_rows %>%
  mutate(source = 'NLDAS-2',
         delta.t = 1)

precip.imerge <- list.files(path = 'data/precipitation/imerge/verified', 
                           pattern = '^imerge.*.csv', full.names = T) %>%
  map(read_csv) %>%
  bind_rows %>%
  mutate(source = 'IMERG-Early',
         delta.t = 0.5,
         precipitation = precipitation * delta.t) # mm/hr to mm

precip.imergf <- list.files(path = 'data/precipitation/imergf/verified', 
                           pattern = '^imergf.*.csv', full.names = T) %>%
  map(read_csv) %>%
  bind_rows %>%
  mutate(source = 'IMERG-Final',
         delta.t = 0.5,
         precipitation = precipitation * delta.t) # mm/hr to mm

precip <- bind_rows(precip.imergf, precip.imerge, precip.mrms, precip.nldas) %>%
  filter(slide.id %in% pull(slide, slide.id),
         as_date(datetime) >= ymd('2015-06-01'),
         as_date(datetime) < ymd('2018-06-30')) %>%
  mutate(precipitation = ifelse(is.na(precipitation), 0, precipitation),
         source = as_factor(source))

precip <- precip %>%
  mutate(source = as_factor(source),
         source = fct_recode(source, `IMERG-Final` = 'IMERG-Final', 
                              `IMERG-Early` = 'IMERG-Early'))
precip %>% summary
```

```{r}
precip.slide.date <- precip %>%
  left_join(slide, by='slide.id') %>%
  filter(as_date(slide.date) == as_date(datetime)) 
precip.slide.date %>%
  group_by(slide.id, source) %>%
  summarize(precipitation = ifelse(precipitation > threshold * delta.t, precipitation, 0),
            precipitation = sum(precipitation),
            is.exact = all(is.exact)) %>%
  mutate(no.precip = precipitation == 0) %>%
  group_by(slide.id) %>%
  summarize(no.precip = all(no.precip),
            is.exact = all(is.exact)) %>% 
  count(no.precip, is.exact)
```

### Check that precipitation is available for landslide dates
```{r}
precip %>%
  inner_join(slide, by=c('slide.id', 'datetime' = 'slide.date')) %>%
  right_join(slide, by=c('slide.id'))
```

# Storms

## Identify all storms
```{r group_precipitation}
precip.groups <- precip %>%
  group_by(slide.id, source) %>%
  # Ignore precipitation below threshold
  mutate(precipitation = ifelse(precipitation > threshold * delta.t, precipitation, 0),
         # Ignore gaps less than 24 hours
         sum_12h.r = rollapply(precipitation, 12 / unique(delta.t), sum, align = 'right', partial = T),
         sum_12h.l = rollapply(precipitation, 12 / unique(delta.t), sum, align = 'left', partial = T),
         # Eliminate float arithmetic errors
         sum_12h.r = ifelse(sum_12h.r < 1e-3, 0, sum_12h.r),
         sum_12h.l = ifelse(sum_12h.l < 1e-3, 0, sum_12h.l),
         # Mark the start of each storm by changing the index
         is.storm.r = sum_12h.r > 0,
         is.storm.l = sum_12h.l > 0,
         storm.start.id = cumsum((is.storm.r - lag(is.storm.r, default = F)) > 0),
         storm.end.id = cumsum((is.storm.l - lag(is.storm.l, default = F)) < 0)) %>%
  # Filter out groupings with no precipitation
  group_by(slide.id, source, storm.start.id, storm.end.id) %>%
  filter(any(precipitation > 0 )) %>%
  left_join(slide.allprecip %>% select(slide.id, slide.date), by=c('slide.id')) %>%
  # Mark landslide-triggering precipitation
  mutate(is.trigger = any(as_date(datetime) == as_date(slide.date))) %>%
  rename(storm.id = storm.start.id) %>%
  ungroup
```

## Calculate storm characteristics
```{r calc_storm_characteristics}
calc.storm.characteristics <- function (precip) {
  precip %>%
    # Calculate storm characteristics
    summarize(depth = sum(precipitation),
              duration = sum(delta.t),
              delta.t = unique(delta.t),
              intensity = depth / duration,
              peak_intensity = max(precipitation / delta.t, na.rm =T),
              start.datetime = min(datetime),
              end.datetime = max(datetime) + dhours(delta.t),
              is.trigger = any(is.trigger)) %>%
    ungroup
}

storm.all <- precip.groups  %>%
  group_by(slide.id, source, storm.id) %>%
  calc.storm.characteristics
```

## Calculate triggering storm characteristics
```{r}
precip.trigger <- precip.groups %>%
  # Select groups overlapping landslide date
  group_by(slide.id, storm.id, source) %>%
  filter(any(as_date(datetime) == as_date(slide.date)),
         # Remove precipitation from after the landslide
         as_date(datetime) <= as_date(slide.date)) %>% 
  ungroup

# Calculate storm characteristics
storm.trigger <- precip.trigger %>%
  group_by(slide.id, source) %>%
  calc.storm.characteristics
storm.trigger %>% summary
precip.trigger
```

## Filter landslides by precipitation occurrence
```{r}
slide <- slide.allprecip %>%
  filter(slide.id %in% unique(storm.trigger$slide.id))

# Save included landslide locations for GIS use
write_csv(slide %>% select(slide.id, lon, lat), 
          file = 'data/landslide/landslide.included.csv')
```

## What data are missing?

```{r}
storm.all %>%
  mutate(duration2 = as.numeric(start.date %--% end.date, "hours")) %>%
  select(slide.id, source, start.date, end.date, duration, duration2, depth) %>%
  filter(duration != duration2)
```

```{r}
precip %>%
  filter(source == 'IMERG-Final', slide.id == 7392, 
         datetime > ymd(20150719), datetime <= ymd(20150721),
         precipitation > delta.t * threshold)
```
```{r}
precip %>%
  left_join(slide, by = 'slide.id') %>%
  filter(as_date(datetime) == as_date(slide.date)) %>%
  filter(precipitation > 1) %>%
  group_by(source, slide.id) %>%
  summarize(precipitation = sum(precipitation)) %>% 
  summary
```

```{r}
precip %>%
  anti_join(storm) %>%
  group_by(slide.id, source) %>%
  summarize(missing = T) %>%
  group_by(source) %>%
  count()
```

## Download frequency

```{r download_frequencies}
get.frequency <- function (lat, lon, layer, depth, nc, ari.v, lon.v, lat.v) {
  ## Subset the precipitation frequency data
  # Calculate the spacing between grid points.
  cell.size <- mean(diff(lat.v))
  # Find the index for the location
  y <- round((lat - min(lat.v)) / cell.size) + 1
  x <- round((lon - min(lon.v)) / cell.size) + 1
  
  # Read data
  if (x > length(lon.v) | y > length(lat.v)) {return(NA)}
  depths <- ncvar_get(nc, layer, c(1, x, y), c(length(ari.v), 1, 1))
  if (is.na(depths[1])) {return(NA)}
  depth.i <- which.min(abs(depths - depth))
  ari.v[depth.i]
}

get.frequencies <- function (lat, lon, layer, depth) {
  # Open a connection to the dataset
  nc <- nc_open('https://hdsc.nws.noaa.gov/thredds/dodsC/data/NOAA_Atlas_14_CONUS.nc')
  ## Query the axes data (lat, lon, ari)
  ari.v <- ncvar_get(nc,'ari')
  lon.v <- ncvar_get(nc, 'lon')
  lat.v <- ncvar_get(nc, 'lat')
  frequencies <- pmap_dbl(list(lat, lon, layer, depth), 
                          ~get.frequency(..1, ..2, ..3, ..4, 
                                         nc, ari.v, lon.v, lat.v))
  nc_close(nc)
  frequencies
}

get.return.periods <- function (precip) {
  precip %>%
    group_by(slide.id, source) %>%
    summarize(pf_168_hr = max(rollsum(precipitation, 168 / unique(delta.t), na.pad = T), na.rm = T),
              pf_096_hr = max(rollsum(precipitation,  96 / unique(delta.t), na.pad = T), na.rm = T),
              pf_072_hr = max(rollsum(precipitation,  72 / unique(delta.t), na.pad = T), na.rm = T),
              pf_048_hr = max(rollsum(precipitation,  48 / unique(delta.t), na.pad = T), na.rm = T),
              pf_024_hr = max(rollsum(precipitation,  24 / unique(delta.t), na.pad = T), na.rm = T),
              pf_012_hr = max(rollsum(precipitation,  12 / unique(delta.t), na.pad = T), na.rm = T),
              pf_006_hr = max(rollsum(precipitation,   6 / unique(delta.t), na.pad = T), na.rm = T),
              pf_003_hr = max(rollsum(precipitation,   3 / unique(delta.t), na.pad = T), na.rm = T),
              pf_002_hr = max(rollsum(precipitation,   2 / unique(delta.t), na.pad = T), na.rm = T),
              pf_001_hr = max(rollsum(precipitation,   1 / unique(delta.t), na.pad = T), na.rm = T)) %>%
    gather(key = 'layer', value = 'depth', -slide.id, -source) %>%
    filter(depth > -Inf) %>%
    left_join(slide, by = c('slide.id')) %>%
    mutate(depth.in = depth / 25.4,
           return.period = get.frequencies(lat, lon, layer, depth.in)) 
}

storm.period.trigger.all <- precip.trigger %>%
  get.return.periods 

storm.period.trigger <- storm.period.trigger.all %>%
  group_by(slide.id, source) %>%
  summarize(return.period = max(return.period)) %>%
  dplyr::select(slide.id, source, return.period) %>%
  left_join(trigger.storm, by=c('slide.id', 'source')) %>%
  left_join(slide %>% dplyr::select(slide.id, is.exact), by='slide.id') %>%
  ungroup()

storm.freq.max1 <- storm.freq.max %>%
  mutate(source = str_replace(source, ' ', '-'))

storm.period.trigger <- storm.trigger %>%
  left_join(storm.freq.max1 %>% select(slide.id, source, return.period),
            by=c('slide.id', 'source')) %>%
  left_join(slide %>% dplyr::select(slide.id, is.exact), by='slide.id') %>%
  ungroup()

storm.period.trigger %>%
  filter(!is.na(return.period)) %>%
  group_by(slide.id) %>%
  summarize(all.2year = all(return.period==2)) %>%
  group_by(all.2year) %>%
  tally()
  
```

# Analysis
## Landslide dataset characteristics
### How many landslides of each type?
```{r slide_types}
# Find landslide type distribution
slide %>%
  group_by(type) %>%
  summarise(n = n(),  percentage = n() / nrow(slide) * 100)
```

### How many landslides of each location accuracy?
```{r slide_accuracy}
slide %>%
  filter(!is.exact) %>%
  group_by(location_accuracy) %>%
  summarise(n = n(),  percentage = n() / nrow(slide) * 100)
```
## Map landslide sites

```{r load_topo}
topo.raster <- raster('data/na_elevation.tif')
topo.df <- as.data.frame(topo.raster, xy=T, na.rm=T) 
topo.df.cut <- topo.df %>%
  mutate(na_elevation = ifelse(na_elevation > 3000, 3000, na_elevation))
```

```{r load_boundaries}
boundaries <- readOGR("data/boundaries", "boundaries_wgs84")
boundaries_df <- fortify(boundaries)
```

```{r plot_map}
ocean.col <- 'turquoise3'
n.verified <- slide %>% filter(is.exact) %>% nrow
n.approx <- slide %>% filter(!is.exact) %>% nrow 
landslide.labels <- c(`TRUE` = str_c('Verified landslide\nlocation (n=', n.verified, ')'),
                      `FALSE`=str_c('Approximate landslide\nlocation (n=', n.approx, ')'))
ggplot() +
  borders(database = 'world', regions = c('Canada', 'USA', 'Mexico'), 
          fill='white', colour=NA) +
  geom_raster(data = topo.df.cut, aes(x = x, y = y, fill = na_elevation)) +
  geom_path(data = boundaries_df, 
            aes(x = long, y = lat, group = group),
            color = 'black', size = .2) +
  borders(database = 'world', regions = c('Canada', 'USA', 'Mexico'), 
          fill=NA, colour='black', size=0.6) +
  borders(database = 'lakes', 
          fill=ocean.col, colour='black', size=0.6) +
  geom_point(data = slide %>% arrange(is.exact), 
             aes(x = lon, y = lat, shape = is.exact, color = is.exact),
             stroke=1) +
  scale_shape_manual('Landslide locations (n=177)', 
                     values = c(`FALSE`=3, `TRUE`=4),
                     labels = landslide.labels) +
  scale_color_manual('Landslide locations (n=177)',
                     values = c(`FALSE`='blue', `TRUE`='white'),
                     labels = landslide.labels) +
  scale_fill_gradientn('Elevation (m)', colors=terrain.colors(10)[2:10],
                       na.value=ocean.col) +
  theme_bw() +
  labs(x = '', y = '') +
  coord_cartesian(ylim = c(24, 57), xlim = c(-140, -60), expand = F) +
  guides(shape = guide_legend(order = 2),
         color = guide_legend(order = 2),
         fill = guide_colorbar(order = 1)) +
  theme(panel.grid = element_blank(), 
        panel.background = element_rect(fill=ocean.col),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = c(0.17, 0.32),
        legend.key = element_rect(fill = terrain.colors(10)[[2]]),
        legend.spacing.y = unit(5, "pt"))
ggsave('..figures/site_map.png', width = 7, height = 4.5)
ggsave('..figures/figure_1_site_map.tiff', width = 7, height = 4.5, dpi = 600)
```

## Landslide type precipitation distribution validation
```{r type_distributions, fig.height = 2, fig.width = 4}
storm.slide.type <- storm.trigger %>%
  left_join(slide, by='slide.id')  %>%
  transmute(slide.id, source, type, `Intensity (mm/h)` = intensity, `Duration (h)` = duration) %>%
  pivot_longer(c(`Intensity (mm/h)`, `Duration (h)`)) %>%
  ungroup
storm.slide.type.summary <- storm.slide.type %>%
  group_by(type, name) %>%
  summarize(max = max(value), value = mean(value))
storm.slide.type %>%
  ggplot() +
  facet_wrap(vars(name), scales = 'free', strip.position = 'bottom') +
  geom_density(aes(x=value, group=type, fill=type),
               alpha = 0.5, color = 'black') +
  geom_vline(data = storm.slide.type.summary,
             aes(xintercept = value, color = type)) +
  geom_text(data = storm.slide.type.summary %>%
              group_by(name) %>%
              summarize(max = max(max)) %>%
              mutate(label = c('a', 'b'), y = c(.75, 1)),
            aes(x = max, y = y, label = label)) +
  theme_bw() +
  scale_x_log10() +
  labs(x = '', y = '', color = 'Landslide type:', fill = 'Landslide type:') +
  theme(strip.placement = "outside",
        axis.text.y = element_blank(),
        strip.background = element_blank(),
        legend.position = 'bottom')
ggsave('..figures/type_distribution.png', width = 8, height = 4)
ggsave('..figures/figure_2_type_distribution.tiff', width = 8, height = 4, dpi=300)
```

```{r type_validation, fig.width=3, fig.height = 1.5 }
storm.all %>% 
    left_join(slide, by = 'slide.id') %>%
    mutate(ifelse(type=='debris_flow', 'mudslide', type),
           ifelse(!(type %in% c('landslide', 'mudslide', 'rock_fall')), 'landslide', type)) %>%
    filter(type %in% c('landslide', 'mudslide', 'rock_fall')) %>%
    droplevels() %>%
    ggplot() +
    facet_wrap(facets =vars(source), nrow =2) +
    facet_grid(cols = vars(source)) +
    geom_point(aes(x = duration, y = intensity, color = type), alpha = 0.8) +
    scale_x_log10('Duration (h)') +
    scale_y_log10('Intensity (mm/h)') +
    scale_color_brewer('', 
                       palette = 'Paired', 
                       labels = c('true'='Landslide-triggering storms',
                                  'false'='All storms 2015-2020')) +
    scale_alpha_manual('',
                       values = c('true'=0.8,'false'=0.1),
                       labels = c('true'='Landslide-triggering storms',
                                  'false'='All storms 2015-2020'),
                       guide = F)  +
    labs(linetype='Intensity-Duration Threshold:') +
    theme_bw() +
    theme(strip.background = element_rect(fill=strip.background),
          legend.position = 'bottom')

ggsave('..figures/type_validation.png', width = 12, height = 8)
```

## Cumulative precipitation at example sites
```{r landslide_precip, fig.width = 5, fig.height = 4}
slide.subset <- tibble(slide.id = c(7761, 8992, 10426, 9123, 10422),
                       interpretation = c('All products are similar',
                                          'Products are correlated but volume is off',
                                          'Total depth matches; intermediate diverges',
                                          'IMERG-Early outlier',
                                          'No landslide trigger detected')) %>%
  left_join(slide.allprecip, by='slide.id') %>%
  mutate(details = as_factor(str_c('Date: ', as_date(slide.date), 
                                   ' -- Location: (', 
                                   round(lat, 1), ', ', 
                                   round(lon, 1), ')')),
         label = c('a', 'b', 'c', 'd', 'e'),
         event_title = as_factor(event_title))

labels <- precip %>%
  right_join(slide.subset, by='slide.id') %>%
  filter(datetime < as_datetime(slide.date),
         datetime > as_datetime(slide.date - days(30))) %>%
  group_by(source, slide.id) %>%
  mutate(precipitation = ifelse(is.na(precipitation), 0, precipitation),
         precipitation = cumsum(precipitation)) %>%
  group_by(slide.id) %>%
  summarize(label = unique(label), x = min(datetime), y = max(precipitation) * 0.9,
            event_title = unique(event_title), details = unique(details))

precip %>%
  filter(slide.id %in% slide.subset$slide.id) %>%
  inner_join(slide.subset, by='slide.id') %>%
  group_by(source, slide.id) %>%
  filter(datetime < as_datetime(slide.date),
         datetime > as_datetime(slide.date - days(30))) %>%
  mutate(precipitation = ifelse(is.na(precipitation), 0, precipitation),
         precipitation = cumsum(precipitation)) %>%
  ggplot() +
  facet_wrap(vars(details), ncol=2, scales='free') +
  geom_line(aes(x = datetime, y = precipitation, group = source, color = source), size=1.5, alpha = 0.6) +
  geom_vline(data = slide.subset, 
             aes(xintercept = as_datetime(slide.date))) +
  geom_label(data = labels, aes(label=label, x=x, y=y)) +
  labs(y = 'Cumulative precipitation (mm)', x = '', color = 'Data Source:') +
  guides(color=guide_legend(keywidth=unit(.1, 'npc'), keyheight=unit(.04, 'npc'))) +
  theme_bw() +
  theme(legend.position = c(0.7, .15),
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"))
ggsave('..figures/example_landslide_precipitation.png', width = 10, height = 8)
ggsave('..figures/figure_3_cumulative_precip.tiff', width = 10, height = 8, dpi = 600)
```

## Rank and z-score

```{r}
precip.summary <- precip %>%
  right_join(slide %>% dplyr::select(slide.id, slide.date), by = 'slide.id') %>%
  mutate(date = as_date(datetime),
         day.of.landslide = date == as_date(slide.date)) %>%
  group_by(slide.id, source, date, day.of.landslide) %>% # Daily precip
  summarize(precipitation = sum(precipitation)) %>% 
  group_by(slide.id, date) %>% # Get rank
  mutate(rank = rank(precipitation)) %>%
  filter(precipitation > 0) %>% # Calculate z-scores
  group_by(slide.id, source) %>%
  mutate(z.score = scale(precipitation)) %>%
  dplyr::select(slide.id, source, date, day.of.landslide, # Prepare for plotting
                precipitation, rank, z.score) %>%
  gather("statistic", "value", -slide.id, -source, -date, -day.of.landslide)  %>%
  mutate(statistic = as_factor(statistic),
         source = as_factor(source),
         day.of.landslide = ifelse(day.of.landslide, 'Day of landslide', 'All days')) %>%
  ungroup()
precip.summary
```

```{r plot_summary}
plot.summary <- function (stat, y.label, labels=c('a', 'b')) {
  label.df <- precip.summary %>% 
    filter(statistic == stat) %>%
    mutate(y = max(value)) %>%
    group_by(day.of.landslide, y) %>%
    summarize(x = fct_unique(source)[[4]]) %>%
    ungroup %>%
    mutate(facet_label=labels)
  precip.summary %>%
  filter(statistic == stat) %>%
  ggplot() +
  facet_grid(rows = vars(day.of.landslide)) +
  geom_boxplot(aes(x=source, y=value, fill=source)) +
  geom_label(data = label.df, aes(x = x, y = y, label = facet_label),
             hjust = -0.5) +
  scale_fill_discrete(guide=F) +
  coord_flip() +
  theme_bw() +
  labs(y=y.label, x='') +
  theme(axis.text.x = element_text(angle=90, hjust=1))
}

```

```{r summary_combo, fig.height= 2, fig.width = 5}
plot.rank <- plot.summary('rank', 'Rank among four products') +
  theme(strip.text = element_blank()) +
  scale_y_continuous(expand=expand_scale(mult=c(0.05, 0.1)), 
                     labels=function (x) sprintf("%3.0f", x))
plot.z <- plot.summary('z.score', 'z-score for product among all dates', c('c', 'd')) +
  scale_y_continuous(expand=expand_scale(mult=c(0.05, 0.1)), trans='pseudo_log') +
  theme(axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        strip.background = element_rect(fill=strip.background))
plot_grid(plot.rank, plot.z, nrow = 1)
ggsave('..figures/summary.png', width = 10, height = 4)
ggsave('..figures/figure_4_summary.tiff', width = 10, height = 4, dpi = 300)
```

## Product comparison against ensemble mean
```{r}
calc.means <- function (d) {
  d %>%
    dplyr::select(slide.id, storm.id, source, is.exact, 
                  depth, duration, return.period, intensity, peak_intensity) %>%
    pivot_longer(c(-slide.id, -storm.id, -source, -is.exact), names_to='measurement') %>%
    mutate(measurement = fct_recode(measurement,
                                    `Depth (mm)` = 'depth',
                                    `Duration (h)` = 'duration',
                                    `Return period (y)` = 'return.period',
                                    `Total intensity (mm/h)` = 'intensity',
                                    `Peak intensity (mm/h)` = 'peak_intensity')) %>%
    group_by(slide.id, storm.id, measurement) %>%
    mutate(ensemble.mean = mean(value, na.rm=T)) 
}

plot.scatter <- function (data, all.data, labels = c('a', 'b', 'c', 'd', 'e'),
                          point.alpha = 0.6) {
  plt <- data %>%
    ggplot() +
    facet_wrap(facets = vars(measurement), nrow = 1, 
               scales = 'free',
               labeller = label_wrap_gen()) +
    geom_abline() +
    geom_point(aes(x = ensemble.mean, y = value, color = source), alpha=point.alpha, size=0.3) +
    geom_point(data = all.data,
               aes(x = value, y = value), alpha = 0)  +
    geom_smooth(aes(x = ensemble.mean, y = value, group = source, color = source, fill = source), 
                alpha = 0.3, method = 'lm', formula = 'y ~ x') +
    scale_fill_discrete(guide = F) +
    scale_x_log10() + scale_y_log10(labels=function (x) sprintf("%.0f", x)) +
    theme_bw() +
    labs(x = 'Ensemble mean', y = 'Individual product value', color = '')
  lay <- ggplot_build(plt)$layout
  scales.x <- lay$panel_scales_x
  scales.y <- lay$panel_scales_y
  label.df <- tibble(x = map_dbl(scales.x, ~10^(.$range$range[1])), 
                     y = map_dbl(scales.y, ~10^(.$range$range[2])),
                     facet_label = labels,
                     measurement = fct_unique(data$measurement))
  plt + 
    geom_label(data = label.df, aes(x = x, y = y, label = facet_label),
               vjust = 1, hjust = 0)
}
```

```{r plot_scatter_all_trigger, fig.height=1.5, fig.width=6}
scatter.trigger <- storm.period.trigger %>%
    dplyr::select(slide.id, source, is.exact, 
                  depth, duration, return.period, intensity, peak_intensity) %>%
    pivot_longer(c(-slide.id, -source, -is.exact), names_to='measurement') %>%
    mutate(measurement = fct_recode(measurement,
                                    `Depth (mm)` = 'depth',
                                    `Duration (h)` = 'duration',
                                    `Return period (y)` = 'return.period',
                                    `Total intensity (mm/h)` = 'intensity',
                                    `Peak intensity (mm/h)` = 'peak_intensity')) %>%
    group_by(slide.id,measurement) %>%
    mutate(ensemble.mean = mean(value, na.rm=T)) 
storm.period.trigger %>% summary
scatter.trigger %>% summary
plot.scatter(scatter.trigger, scatter.trigger)
ggsave('..figures/scatter_ensemble_mean.png', width = 12, height = 3)
```

```{r plot_scatter_exact_trigger, fig.height=1.5, fig.width=6}
plot.scatter(scatter.trigger %>% filter(is.exact), scatter.trigger)
ggsave('..figures/scatter_ensemble_mean_exact.png', width = 12, height = 3)
storm.trigger %>% summary
```

```{r plot_scatter_all, fig.height=1.5, fig.width=6}
scatter <- storm.all %>% 
  right_join(slide %>% select(slide.id, is.exact), by='slide.id') %>%
  mutate(return.period = NA)%>%
  dplyr::select(slide.id, storm.id, source, is.exact, 
                depth, duration, return.period, intensity, peak_intensity) %>%
  pivot_longer(c(-slide.id, -storm.id, -source, -is.exact), names_to='measurement') %>%
  mutate(measurement = fct_recode(measurement,
                                  `Depth (mm)` = 'depth',
                                  `Duration (h)` = 'duration',
                                  `Return period (y)` = 'return.period',
                                  `Total intensity (mm/h)` = 'intensity',
                                  `Peak intensity (mm/h)` = 'peak_intensity')) %>%
  group_by(slide.id, storm.id, measurement) %>%
  mutate(ensemble.mean = mean(value, na.rm=T)) %>%
  filter(measurement != 'Return period (y)') %>%
  droplevels()

plot.scatter(scatter, scatter, point.alpha = 0.1, labels = c('k', 'l', 'm', 'n'))
ggsave('..figures/scatter_ensemble_mean.png', width = 12, height = 3)
```

```{r plot_scatter_combo, fig.height=2.5, fig.width=4.5}
scatter.minmax <- scatter %>% 
  group_by(measurement) %>% 
  filter(value %in% c(min(value), max(value))) %>% 
  group_by(measurement, value) %>%
  summarize()

# Legend
scatter.legend <- plot.scatter(scatter.trigger, scatter.minmax) +
  labs(y = '') +
  theme(strip.background = element_rect(fill=strip.background))
scatter.legend <- cowplot::get_legend(scatter.legend)

# Top row: all triggering storms
scatter.all.plot <- plot.scatter(scatter.trigger, scatter.minmax) +
  labs(x = '', y = '') +
  theme(legend.position = "none",
        strip.text.y = element_text(),
        strip.background = element_rect(fill=strip.background))
scatter.all.label <- ggdraw() +
  draw_grob(rectGrob(gp = gpar(fill = strip.background),
                     height = unit(0.8, "npc"), vjust = 0.44)) +
  draw_label("All landslide locations", colour = 'black',
             x = 0.1, vjust = -0.2, hjust = 0.525, angle = -90, size=8)
scatter.all <- plot_grid(scatter.all.plot, scatter.all.label, 
                         nrow = 1, rel_widths = c(1, 0.024))


# Middle row: exact locations
scatter.exact.plot <- plot.scatter(scatter.trigger %>% filter(is.exact), 
                                   scatter.minmax,
                                   labels = c('f', 'g', 'h', 'i', 'j')) +
  labs(x = '', y = '') +
  theme(legend.position='none',
        strip.text = element_blank())
scatter.exact.label <- ggdraw() +
  draw_grob(rectGrob(gp = gpar(fill = strip.background),
                     height = unit(0.9, "npc"), vjust = 0.5)) +
  draw_label("Verified landslide locations", colour = 'black',
             x = 0.1, vjust = -0.2, hjust = 0.525, angle = -90, size=8)
scatter.exact <- plot_grid(scatter.exact.plot, scatter.exact.label, 
                           nrow = 1, rel_widths = c(1, 0.024))
# Bottom row: all storms 
scatter.clim.plot <- plot.scatter(scatter, scatter.minmax %>% 
                                    filter(measurement != 'Return period (y)') %>% 
                                    droplevels, 
                                  point.alpha = 0.1, 
                                  labels = c('k', 'l', 'm', 'n')) +
  labs(y = '') +
  theme(legend.position='none',
        strip.text = element_blank())
scatter.clim.label <- ggdraw() +
  draw_grob(rectGrob(gp = gpar(fill = strip.background),
                     height = unit(0.8, "npc"), vjust = 0.44)) +
  draw_label("Climatology 2015-2018", colour = 'black',
             x = 0.1, vjust = -0.2, hjust = 0.55, angle = -90, size=8)
scatter.clim <- plot_grid(scatter.clim.plot, scatter.clim.label, scatter.legend,
                          nrow = 1, rel_widths = c(4, 0.12, 1))

scatter.y.axis <- ggdraw() +
  draw_label("Individual product value", size = 12,
             x = 0.1, vjust = 1, hjust = 0.4, angle = 90)
scatter.plots <- plot_grid(scatter.all, scatter.exact, scatter.clim,  
                           rel_heights = c(3, 2.7, 2.7), ncol = 1)
plot_grid(scatter.y.axis, scatter.plots,
          nrow = 1, rel_widths = c(0.015, 1))
ggsave('..figures/scatter_ensemble_mean.png', width = 9, height = 5)
ggsave('..figures/figure_5_scatter.tiff', width = 9, height = 5, dpi=600)
```

```{r percent_difference}
storm.freq.pctdiff <- storm.period.trigger %>%
  calc.means %>%
  filter(measurement %in% c('Depth (mm)', 'Duration (h)')) %>%
  mutate(percent.difference = (value - ensemble.mean) / ensemble.mean * 100,
         is.exact = ifelse(is.exact, 'Exact location', 'Approximate location'))

storm.freq.pctdiff %>%
  group_by(measurement) %>%
  mutate(median.pctdiff = median(abs(percent.difference))) %>%
  group_by(measurement, is.exact) %>%
  mutate(gt.median = abs(percent.difference) > median.pctdiff,
         gt.median = ifelse(gt.median, 'gt.median', 'lt.median')) %>%
  group_by(measurement, is.exact, gt.median) %>%
  tally() %>% 
  pivot_wider(c('measurement', 'is.exact'), names_from = gt.median, values_from = n) %>%
  mutate(pct.gt.median = gt.median / (gt.median + lt.median) * 100)

storm.freq.pctdiff %>%
  ggplot() +
  facet_wrap(c('measurement'), nrow = 1) +
  geom_boxplot(aes(x = is.exact, y = abs(percent.difference))) +
  theme_minimal() +
  labs(x = '', y = 'Absolute percent difference from mean')
```

## Return period vs. Peak intensity

```{r fig.width=2, fig.height=2}
storm.period.trigger %>%
  drop_na(return.period) %>%
  ggplot(aes(x = peak_intensity, y = return.period)) +
  geom_point() +
  theme_minimal() +
  scale_y_log10() +
  geom_smooth(method = 'glm', formula = 'y~x', se=F, 
              color='black') +
  labs(x='Peak Intesity (mm/h)', y = 'Return period (y)') +
  theme(legend.position = 'bottom')

ggsave('..figures/scatter_peakintensity_period.png', width = 4, height = 4)
ggsave('..figures/figure_6_scatter_peakintensity_period.tiff', width = 4, height = 4, dpi=300)
```

```{r}
storm.freq.max %>%
  ggplot() +
  facet_wrap(vars(source), nrow=1) +
  geom_boxplot(aes(x=as_factor(return.period), y=peak_intensity, fill=source)) +
  geom_text(data = storm.freq.max %>%
              group_by(source, return.period) %>% 
              summarize(n=n()),
            aes(x = as_factor(return.period), y = 90, label = str_c('n=', n)), 
            angle=90, size=3, hjust=1) +
  scale_fill_discrete(guide=F) +
  theme_bw() +
  labs(x='Storm return period (years)', y = 'Peak intensity (mm/h)', fill='Dataset:') +
  theme(axis.text.x = element_text(angle=90, hjust = 1))
ggsave('..figures/frequency_peak.png', width = 6, height = 4)
```

## Intensity-duration threshold

### Intensity-duration figures
```{r plot_id_threshold}
storm.max.duration <- storm.all %>%
  pull(duration) %>%
  max
storm.min.duration <- storm.all %>%
  pull(duration) %>%
  min
id.thresholds <- tibble(
      model = as.factor(c('Guzzetti et al. (2008) Csa', 
                          'Guzzetti et al. (2008) Csb', 
                          'Crosta and Frattini (2001)',
                          'Clarizia et al. (1996)')),
      beta0 =        c(0,     0,     0.48,  0),
      beta1 =        c(4.81,  3.57, 7.2,   10),
      beta2 =        c(-0.49, -0.41, -1.0,  -0.77),
      min.duration = c(0.1,   0.167,  0.1,  0.1),
      max.duration = c(1000,  500,    1000, 1000),
      restriction = c('csa', 'csb', 'both', 'landslide'),
      facet.row = c('koppen', 'koppen', 'type', 'type')
    ) %>%
  mutate(min.duration = max(min.duration, storm.min.duration),
         max.duration = min(max.duration, storm.max.duration),
         func = pmap(list(beta0, beta1, beta2), 
                     ~function (d) beta0 + beta1*d^beta2),
         geom = pmap(list(model, restriction, 
                          beta0, beta1, beta2, 
                          min.duration, max.duration),
                     ~geom_function(aes(x = duration, linetype = ..1, 
                                        color = str_c('true.', ..2)), 
                                    fun=function (d) ..3 + ..4*d^..5)))

plot.idthresh <- function (data, thresholds, labels=c('a', 'b', 'c', 'd')) {
  plt <- data %>% 
    left_join(slide, by = 'slide.id') %>%
    #filter(lon < -115) %>%
    arrange(is.trigger) %>% 
    mutate(is.trigger = ifelse(is.trigger, 'true', 'false')) %>%
    ggplot() +
    facet_grid(cols = vars(source)) +
    geom_point(aes(x = duration, y = intensity, 
                   color = interaction(is.trigger, restriction),
                   alpha = is.trigger)) +
    list(thresholds$geom) +
    scale_x_log10('Duration (h)',
                  breaks = c(1, 12, 24, 100, 1000)) +
    scale_y_log10('Intensity (mm/h)') +
    scale_color_brewer('', 
                       palette = 'Paired', 
                       breaks = c('true.csa',
                                  'false.csa',
                                  'true.csb',
                                  'false.csb',
                                  'true.landslide',
                                  'false.landslide',
                                  'true.mudslide',
                                  'false.mudslide',
                                  'true.both'),
                       labels = c('true.csa'='Landslide-triggering storms (Csa)',
                                  'false.csa'='All storms 2015-2018 (Csa)',
                                  'true.csb'='Landslide-triggering storms (Csb)',
                                  'false.csb'='All storms 2015-2018 (Csb)',
                                  'true.landslide'='Landslide triggering storms (Landslide)',
                                  'false.landslide'='All storms 2015-2018 (Landslide)',
                                  'true.mudslide'='Landslide triggering storms (Mudslide or debris flow)',
                                  'false.mudslide'='All storms 2015-2018 (Mudslide or debris flow)',
                                  'true.both'='Landslide or mudslide'),
                       drop = F,
                       guide = guide_legend(ncol= 2, byrow = 2, 
                                            override.aes = list(linetype=0))) +
    scale_alpha_manual('',
                       values = c('true'=0.8,'false'=0.1),
                       labels = c('true'='Landslide-triggering storms',
                                  'false'='All storms 2015-2020'),
                       guide = F)  +
    scale_linetype_manual(values = c('solid', 'dotted', 'dotdash', 'dashed'),
                          drop=F,
                          guide = guide_legend(ncol= 2, title.position = 'top',
                                               override.aes = list(color = c('#33a02c', #green
                                                                             '#6a3d9a', #purple
                                                                             '#1f78b4', #blue
                                                                             '#e31a1c')))) + #red
    labs(linetype='Intensity-duration thresholds:') +
    theme_bw() +
    theme(strip.background = element_rect(fill=strip.background))
  lay <- ggplot_build(plt)$layout
  scales.x <- lay$panel_scales_x
  scales.y <- lay$panel_scales_y
  label.df <- tibble(x = map_dbl(scales.x, ~10^(.$range$range[2])), 
                     y = map_dbl(scales.y, ~10^(.$range$range[2])),
                     facet_label = labels,
                     source = fct_unique(data$source))
  plt + 
    geom_label(data = label.df, aes(x = x, y = y, label = facet_label),
               vjust = 1, hjust = 1)
}

idthresh.df <- storm.all %>%
  right_join(slide %>% select(slide.id, type, is.exact), by='slide.id') %>%
  mutate(restriction = type, facet.row = 'type') %>%
  filter(type %in% c('Landslide', 'Mudslide or debris flow')) %>%
  bind_rows(storm.all %>%
              right_join(slide %>% select(slide.id, koppen, is.exact), by='slide.id') %>%
              mutate(restriction = koppen, facet.row = 'koppen') %>%
              filter(str_detect(koppen, '^Cs(a|b)'))) %>%
  select(-koppen, -type) %>%
  mutate(facet.row = factor(facet.row),
         restriction = factor(restriction),
         restriction = fct_recode(restriction,
                                  'csa' = 'Csa: Temperate, dry summer, hot summer',
                                  'csb' = 'Csb: Temperate, dry summer, warm summer',
                                  'landslide' = 'Landslide',
                                  'mudslide' = 'Mudslide or debris flow'),
         restriction = fct_relevel(restriction, 'csa', 'landslide', 'csb', 'mudslide'),
         restriction = fct_expand(restriction, 'both')) %>%
  sample_frac()
```
```{r fig.width = 4.5, fig.height = 2}
plot.idthresh(idthresh.df %>% filter(facet.row=='type'),
              id.thresholds %>% filter(facet.row=='type')) + 
  theme(legend.position = 'bottom',
        legend.box="vertical")
```

```{r plot_idt_combo, fig.height=5, fig.width=4}
idt.legend.plt <- plot.idthresh(idthresh.df, id.thresholds) +
  theme(legend.position = 'bottom',
        legend.box="vertical")
idt.legend <- get_legend(idt.legend.plt)

idt.koppen.all.plot <- plot.idthresh(idthresh.df %>% filter(facet.row=='koppen'),
                                     id.thresholds %>% filter(facet.row=='koppen'),
                            labels = c('a', 'b', 'c', 'd')) +
  theme(legend.position = "none",
        axis.title = element_blank())

idt.type.all.plot <- plot.idthresh(idthresh.df %>% filter(facet.row=='type'),
                                     id.thresholds %>% filter(facet.row=='type'),
                            labels = c('e', 'f', 'g', 'h')) +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        strip.background = element_blank(),
        strip.text = element_blank())

idt.all.label <- ggdraw() + 
  draw_grob(rectGrob(gp = gpar(fill = strip.background),
                     height = unit(.8, "npc"), vjust = 0.48)) +
  draw_label("All qualifying landslide locations", colour = 'black',
             x = 0.1, vjust = -0.3, hjust = 0.5, angle = -90, size=12)
idt.all <- plot_grid(plot_grid(idt.koppen.all.plot, idt.type.all.plot, ncol = 1), 
                     idt.all.label, 
                     nrow = 1, rel_widths = c(1, 0.03))

idt.koppen.exact.plot <- plot.idthresh(idthresh.df %>% filter(facet.row=='koppen', is.exact),
                                       id.thresholds %>% filter(facet.row=='koppen'),
                            labels = c('i', 'j', 'k', 'l')) +
  theme(legend.position = "none",
        axis.title = element_blank(),
        strip.background = element_blank(),
        strip.text = element_blank())

idt.type.exact.plot <- plot.idthresh(idthresh.df %>% filter(facet.row=='type', is.exact),
                                     id.thresholds %>% filter(facet.row=='type'),
                            labels = c('m', 'n', 'o', 'p')) +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        strip.background = element_blank(),
        strip.text = element_blank())

idt.exact.label <- ggdraw() +
  draw_grob(rectGrob(gp = gpar(fill = strip.background),
                     height = unit(.84, "npc"), vjust =.44)) +
  draw_label("Verified landslide locations", colour = 'black',
             x = 0.1, vjust = -0.3, hjust = .5, angle = -90, size=12)
idt.exact <- plot_grid(plot_grid(idt.koppen.exact.plot, idt.type.exact.plot, ncol = 1),
                       idt.exact.label, 
                       nrow = 1, rel_widths = c(1, 0.03))

idt.y.axis <- ggdraw() +
  draw_label("Intensity (mm/h)", size = 12,
             x = 0.1, vjust = 1, hjust = 0.2, angle = 90)
idt.plots <- plot_grid(idt.all, idt.exact, idt.legend, 
                           rel_heights = c(3.1, 3, 2), ncol = 1)
plot_grid(idt.y.axis, idt.plots,
          nrow = 1, rel_widths = c(0.025, 1))

ggsave('..figures/intensity_duration.png', width = 8, height = 10)
ggsave('..figures/figure_7_idt.tiff', width = 8, height = 10, dpi=600)
```

## Intensity-duration distribution comparison

```{r fig.width = 4, fig.height = 2.5}
convert.range <- function (range) {
  limits <- 10^as.numeric(str_match_all(range, '-?\\d.\\d\\d')[[1]])
  limits <- round(limits)
  str_c(limits[1], 'h < D < ', limits[2], 'h')
}
storm.all %>%
  mutate(duration.band = cut_width(log10(duration), width = 0.5)) %>%
  mutate(duration.band = fct_relabel(duration.band, ~map_chr(., convert.range))) %>%
  ggplot() +
  facet_wrap(vars(duration.band), nrow = 1)  +
  geom_boxplot(aes(x = source, y = intensity, fill = source)) +
  scale_y_log10()  +
  theme_bw() +
  labs(x = '', fill = '', y = 'Mean intensity (mm/h)') +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = 'bottom')

ggsave('..figures/intensity_duration_distribution.png', width = 8, height = 5)
ggsave('..figures/figure_8_intensity_duration_distribution.tiff', width = 8, height = 5, dpi=300)
```

### Scores

```{r}
calc.threat <- function (data) {
  data %>%
    left_join(id.thresholds, by=c('restriction', 'facet.row')) %>%
    dplyr::select(slide.id, source, is.trigger, intensity, duration) %>%
    merge(id.thresholds) %>%
    dplyr::mutate(threshold.intensity = beta0 + beta1 * duration ^ beta2,
           hit = is.trigger & intensity > threshold.intensity,
           miss = is.trigger & intensity < threshold.intensity,
           false.alarm = !is.trigger & intensity > threshold.intensity,
           true.negative = !is.trigger & intensity < threshold.intensity) %>%
    dplyr::select(-is.trigger, -intensity, -duration) %>%
    dplyr::group_by(source, model) %>%
    dplyr::summarize_at(vars(hit, miss, false.alarm, true.negative), ~sum(., na.rm=T)) %>%
    dplyr::mutate(n = hit + miss,
           hit.ratio = hit / (hit + miss),
           false.alarm.ratio = false.alarm / (false.alarm + true.negative),
           frequency.bias = (hit + false.alarm) / (hit + miss)) %>%
    dplyr::mutate_at(vars(-source, -model), ~round(., digits = 2))
}
idthresh.df %>% group_by(is.exact) %>%tally
calc.threat(idthresh.df %>%
              bind_rows(idthresh.df %>% 
                          filter(restriction %in% c('landslide', 'mudslide')) %>%
                          mutate(restriction = 'both')) %>%
              filter(is.exact)) %>%
  dplyr::select(source, model, hit.ratio, false.alarm.ratio, frequency.bias) %>%
  dplyr::arrange(source, model) %>%
  dplyr::mutate(source = as.character(source), model = as.character(model)) %>%
  stargazer::stargazer(type = "text", summary = F)
```

### Product comparison summary statistics

```{r}
storm.freq.max %>%
  dplyr::select(slide.id, source, depth, duration, frequency, intensity, peak_intensity) %>%
  gather('measurement', 'value', -slide.id, -source) %>%
  group_by(slide.id, measurement) %>%
  summarize(min.value = min(value), max.value = max(value), range = max.value - min.value, n = n()) %>%
  filter(n > 1) %>%
  group_by(measurement) %>%
  summarize(min.range = min(range), max.range = max(range), avg.range = mean(range))
```



```{r fig.height=1, fig.width=5}
trigger.precip%>%
  group_by(slide.id, source) %>%
  summarize(frequency = max(frequency)) %>%
  left_join(storm, by=c('slide.id', 'source')) %>%
  mutate(frequency = 1 / frequency) %>%
  dplyr::select(slide.id, source, depth, duration, frequency, intensity, peak_intensity) %>%
  gather('measurement', 'value', -slide.id, -source) %>%
  mutate(measurement = as_factor(measurement)) %>%
  mutate(measurement = fct_recode(measurement,
                                  `Depth (mm)` = 'depth',
                                  `Duration (h)` = 'duration',
                                  `Frequency (1/yr)` = 'frequency',
                                  `Total intensity (mm/h)` = 'intensity',
                                  `Peak hourly intensity (mm/h)` = 'peak_intensity'))%>%
  ggplot(aes(x = source, y = value, group = source, fill = source)) +
  facet_wrap(facets = vars(measurement), nrow = 1, 
             scales = 'free',
             labeller = label_wrap_gen()) +
  geom_violin() +
  geom_boxplot(width=0.1, fill='white') +
  labs(x = '', y= '') +
  scale_fill_discrete(guide=F) +
  theme_bw()
```

```{r}
trigger.precip %>%
  dplyr::select(slide.id, source, frequency) %>%
  mutate(frequency = as_factor(frequency)) %>%
  ggplot(aes(x = frequency, y = ..prop..,  group = source, fill = source)) +
  geom_bar(position = position_dodge()) +
  theme_minimal() +
  labs(x = 'Return interval', y = 'Proportion of landslide-triggering storms')
ggsave('..figures/frequency_histogram.png', width = 6, height = 4)
```



```{r}
storm.all %>%
  group_by(slide.id) %>%
  
  arrange(is.trigger) %>%
  ggplot(aes(x = duration, y = intensity, color = is.trigger)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  scale_color_manual(values = c(`FALSE`='grey', `TRUE` = 'blue'), guide = F) +
  theme_minimal()
```















